The physiognomy of access to Chilean higher education: The influence of socio-political and personal factors

### 2023-04-05 Paper_Higher_Education.Rmd
Update Paper_Higher_Education.Rmd

---
title: "Influences on the access to higher education: Visualization and modeling for Chilean data"
author: 'Bastian Olea-Duran, Francisco A. Segovia, Nixon Jerez-Lillo, Eduardo Alarcón-Bustamante, Danilo Alvares'
date: "10/08/2021"
output:
  html_document: default
  pdf_document: default
---

>>>>

---
title: "The physiognomy of access to Chilean higher education: The influence of socio-political and personal factors"
author: 'Bastian Olea-Duran, Francisco A. Segovia, Nixon Jerez-Lillo, Eduardo Alarcón-Bustamante, Danilo Alvares'
date: "10/08/2021"
output:
  html_document: default
  pdf_document: default
---
